TODO

### 2021-03-12 publications/The_tool_intro/paper.tex
tool_intro:P4 example

@@

\begin{table*}
\begin{tabular}{|p{3.3cm}|p{5.9cm}|p{7.7cm}|}
\hline
\begin{lstlisting}[basicstyle=\scriptsize]
header ethernet_t {
  macAddr_t dstAddr;
  macAddr_t srcAddr;
  bit<16>   etherType; }

\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\scriptsize]
parser MyParser(...) {
  state start { transition parse_ethernet; }
  state parse_ethernet {
    packet.extract(hdr.ethernet);
    transition select(hdr.ethernet.etherType) {
      TYPE_IPV4: parse_ipv4;
      default: accept; } }
  state parse_ipv4 {
    packet.extract(hdr.ipv4);
    transition accept; } }
control MyIngress(...) {
  apply {
    if (hdr.ipv4.isValid()) {
           ipv4_lpm.apply(); }
  }         
  action drop() {
    mark_to_drop(standard_metadata);
  }    
\end{lstlisting}
&
\begin{lstlisting}[basicstyle=\scriptsize]
  action ipv4_forward(macAddr_t dstAddr, egressSpec_t port) {
    standard_metadata.egress_spec = port;
    hdr.ethernet.srcAddr = hdr.ethernet.dstAddr;
    hdr.ethernet.dstAddr = dstAddr;
    hdr.ipv4.ttl = hdr.ipv4.ttl - 1;
  }    
  table ipv4_lpm {
    key = {  hdr.ipv4.dstAddr: lpm;  }
    actions = {
      ipv4_forward;
      drop;
      NoAction;}
    ... }   
}
control MyDeparser(packet_out packet, in headers hdr) {
  apply {
    packet.emit(hdr.ethernet);
    packet.emit(hdr.ipv4);}
}
\end{lstlisting}\\
\hline
\end{tabular}
\caption{P4 example}
  \label{code:P4}
\end{table*}

@@

>>>>

\lstdefinelanguage{P4}{
  showlines=true,
  morecomment=[f]{//},
  keepspaces=true,
  basicstyle=\scriptsize\ttfamily,
  emphstyle=\itshape,
  emph={},
  commentstyle=\color{red},
  keywordstyle=\color{blue},
  morekeywords={typedef, header, extern, struct, parser, state, transition, in, out, inout, select, default, control, action, table, apply, if, switch}
}

@@

@@

\begin{figure*}
\begin{tabular}{|p{3.3cm}|p{5.9cm}|p{7.7cm}|}
\hline
\begin{lstlisting}[language=P4]
// Definitions
typedef bit<9>  egSpec_t;
typedef bit<48> macAddr_t;
typedef bit<32> ip4Addr_t;

// Headers
header ethernet_t {
  macAddr_t dstAddr;
  macAddr_t srcAddr;
  bit<16>   etherType; }

\end{lstlisting}
&
\begin{lstlisting}[language=P4]
// Parser
parser MyParser(...) {
  state start { transition parse_ethernet; }
  state parse_ethernet {
    packet.extract(hdr.ethernet);
    transition select(hdr.ethernet.etherType) {
      TYPE_IPV4: parse_ipv4;
      default: accept; } }
  state parse_ipv4 {
    packet.extract(hdr.ipv4);
    transition accept; } }

// Control    
control MyIngress(...) {
  apply {
    if (hdr.ipv4.isValid()) {
           ipv4_lpm.apply(); }
  }         
  action drop() {
    mark_to_drop(standard_metadata);
  }    
\end{lstlisting}
&
\begin{lstlisting}[language=P4]
  action ipv4_forward(macAddr_t dstAddr, egSpec_t port) {
    standard_metadata.egress_spec = port;
    hdr.ethernet.srcAddr = hdr.ethernet.dstAddr;
    hdr.ethernet.dstAddr = dstAddr;
    hdr.ipv4.ttl = hdr.ipv4.ttl - 1;
  }    
  table ipv4_lpm {
    key = {  hdr.ipv4.dstAddr: lpm;  }
    actions = {
      ipv4_forward;
      drop;
      NoAction;}
    ... }   
}

//Deparser
control MyDeparser(packet_out packet, in headers hdr) {
  apply {
    packet.emit(hdr.ethernet);
    packet.emit(hdr.ipv4);}
}
\end{lstlisting}\\
\hline
\end{tabular}
\caption{P4 example}
  \label{code:P4}
\end{figure*}
